\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-27 paper/introduction.tex
paper: add references to intro

% Context
Handling incorrect or dirty data is a complex and challenging problem for analysts.
% Problem
One way in which a dataset can be dirty is for parts of it to be missing altogether.
Missing data is one of the simpler variants of dirty data, but if handled naively, can still cause analyses to be incorrect.
According to some estimates, data scientists spend between 50 and 80 percent of their time performing tasks such as collecting and cleaning datasets~\cite{data-science-cleaning}.

% Solution
To handle this problem, users may manually clean their dataset by performing some statistical analysis to replace missing data elements with likely values.
This process is called \emph{imputation}.
We have developed a system called \ProjectName{} with a novel query optimization algorithm which allows imputation to occur on the fly, during query execution. \emph{The key insight behind \ProjectName{} is that imputation
only needs to be performed on the data relevant to a particular query and
that this subset is generally much smaller than the entire database.}

>>>>

% Context
Handling incorrect or dirty data is a complex and challenging problem for analysts.
% Problem
One way in which a dataset can be dirty is for parts of it to be missing altogether~\cite{kim2003}.
Missing data is one of the simpler variants of dirty data, but if handled naively, can still cause analyses to be incorrect~\cite{rubin1976}.
According to some estimates, data scientists spend between 50 and 80 percent of their time performing tasks such as collecting and cleaning datasets~\cite{data-science-cleaning}.

% Solution
To handle this problem, users may manually clean their dataset by performing some statistical analysis to replace missing data elements with likely values.
This process is called \emph{imputation}.
We have developed a system called \ProjectName{} with a novel query optimization algorithm which allows imputation to occur on-the-fly, during query execution. \emph{The key insight behind \ProjectName{} is that imputation
only needs to be performed on the data relevant to a particular query and
that this subset is generally much smaller than the entire database.}
